Composition-climate paper

### 2016-06-17 Composition_Ecology.Rmd
Bib and csl in yaml header moved.

---
output:
  word_document: null
  pdf_document:
    pandoc_args: -V geometry:vmargin=1in -V geometry:hmargin=1in
  md_document:
    variant: markdown_github
csl: ecology.csl
pandoc_args: -H margins.sty
bibliography: goringetal_references.bib
---

>>>>

---
bibliography: goringetal_references.bib
csl: ecology.csl
output:
  word_document: null
  pdf_document:
    pandoc_args: -V geometry:vmargin=1in -V geometry:hmargin=1in
  md_document:
    variant: markdown_github
pandoc_args: -H margins.sty
---
